D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-16 ootavacuous.tex
Outline constraints from non-volatile relaxed atomic stores
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Although C++ non-volatile accesses to atomic objects are not observable
behavior, @@@

In addition,such accesses are still subject to the memory model.
In particular, implementations must not behave as if the source code has
additional:

>>>>

Although C++ non-volatile accesses to atomic objects are not observable
behavior, any implementation that restricts its code analysis to a
single thread must assume (unless it can prove otherwise) that a given
relaxed atomic store might affect observable behavior following any
load that returns the value stored.
This assumption does not constrain the implementation to anywhere near
the extent that a volatile relaxed atomic store would, but it does add
significant constrants over those related to non-volatile non-atomic
stores.

For example, non-volatile relaxed atomic accesses are subject to
the memory model.
In particular, implementations must not behave as if the source code has
additional:
